Statistical analysis of proteomics experiments with R and MSstats (v3.0.9)

### 2015-09-18 MSstats_manual_RMarkdown.Rmd
20150918 : merge Tsung-heng updates

---
title: "Statistical analysis of proteomics experiments with R and MSstats (v3.0.9)"
author: "Meena Choi, Tsung-Heng Tsai & Erik Verschueren"
date: "September 10, 2015"
output: pdf_document
---

@@

```{r, eval=T}
# default option
DDA2009.TMP.random <- dataProcess(raw = DDA2009.superhirn, fillIncompleteRows = TRUE,
                           normalization = 'equalizeMedians',
                           summaryMethod = 'TMP',
                           censoredInt=NULL)
```

@@

### 2. Different option for dataProcess
Additional options in `dataProcess` need to be specified for processing Skyline output are `skylineReport=TRUE` (remove `Truncated=TRUE` rows and handle intensity=0) and `censoredInt="0"` (use intensity=0 as censored to handle missing values).

@@

If you have MaxQuant output, please follow this section. Here controlled mixture data with dynamic range benchmark (Cox, 2014 in MCP) is used to demonstrate.

>>>>

---
title: "Statistical analysis of proteomics experiments with R and MSstats (v3.0.9)"
author: "Meena Choi, Tsung-Heng Tsai & Erik Verschueren"
date: "September 18, 2015"
output: pdf_document
---

@@

```{r, eval=T}
# no action for missing values.
DDA2009.TMP.random <- dataProcess(raw = DDA2009.superhirn, fillIncompleteRows = TRUE,

                           normalization = 'equalizeMedians',
                           summaryMethod = 'TMP',
                           censoredInt=NULL)
```

@@

### 2. Different options for Skyline in dataProcess
Additional options in `dataProcess` need to be specified for processing Skyline output are `skylineReport=TRUE` (remove `Truncated=TRUE` rows and handle intensity=0) and `censoredInt="0"` (use intensity=0 as censored to handle missing values and in this case, NA values are assumed as random missing).

@@

If you have MaxQuant output, please follow this section. Here controlled mixture data with dynamic range benchmark (Cox, 2014 in MCP) is used to demonstrate. This dataset is available in [MSstats material github](https://github.com/MeenaChoi/MSstats_material) in the folder named 'example dataset/DDA_controlledMixture20014'.
